Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-24 RNARedPrint.tex
Updates from ShareLaTeX
fix bracket

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% For instructions on how to fill out this Tex template           %%
%% document please refer to Readme.html and the instructions for   %%
%% authors page on the biomed central website                      %%
%% http://www.biomedcentral.com/info/authors/                      %%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%% BioMed Central currently use the MikTex distribution of         %%
%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
%% http://www.miktex.org                                           %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection*{Expressing \GCb\%-content, sequence validity and energies as features}
Formally, we define a \Def{feature $F$} as a function on sequences, whose value is obtained by summing over an associated set of \Def{contributions}. Each contribution $f$ takes values in $\mathbb{R}\cup \{+\infty\}$, and depends on the nucleotides assigned to a restricted set of positions, its \emph{dependencies $\dep(f)$}, such that
}
$$
F(S) =\!\!\!\!\!\!\!\sum_{\substack{\text{$f$ contribution of $F$,}\\\text{ $\dep(f)=\{x_1,x_2,\ldots\}$}}}\!\!\!\!\!\! f\left(\left\{\substack{x_1\mapsto S_{x_1}\\x_p\mapsto S_{x_2}\\\cdots}\right\}\right).
$$
\revised{Here, since $\dep(f)=\{x_1,\ldots,x_p\}$, $\left\{\substack{x_1\mapsto S_{x_1}\\\cdots\\x_p\mapsto S_{x_p}}\right\}$ denotes the assignment, that assigns to all positions $x_k$  in $\dep(f)$ the respective nucleotide $S_{x_k}$ ($1\leq k\leq p$).}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% For instructions on how to fill out this Tex template           %%
%% document please refer to Readme.html and the instructions for   %%
%% authors page on the biomed central website                      %%https://www.overleaf.com/project/5b98dc8ced90175e9717c15a
%% http://www.biomedcentral.com/info/authors/                      %%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%% BioMed Central currently use the MikTex distribution of         %%
%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
%% http://www.miktex.org                                           %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection*{Expressing \GCb\%-content, sequence validity and energies as features}
Formally, we define a \Def{feature $F$} as a function on sequences, whose value is obtained by summing over an associated set of \Def{contributions}. Each contribution $f$ takes values in $\mathbb{R}\cup \{+\infty\}$, and depends on the nucleotides assigned to a restricted set of positions, its \emph{dependencies $\dep(f)$}, such that

$$
F(S) =\!\!\!\!\!\!\!\sum_{\substack{\text{$f$ contribution of $F$,}\\\text{ $\dep(f)=\{x_1,x_2,\ldots\}$}}}\!\!\!\!\!\! f\left(\left\{\substack{x_1\mapsto S_{x_1}\\x_p\mapsto S_{x_2}\\\cdots}\right\}\right).
$$
\revised{Here, since $\dep(f)=\{x_1,\ldots,x_p\}, $\left\{\substack{x_1\mapsto S_{x_1}\\\cdots\\x_p\mapsto S_{x_p}}\right\}$ denotes the assignment, that assigns to all positions $x_k$  in $\dep(f)$ the respective nucleotide $S_{x_k}$ ($1\leq k\leq p$).}
